Global code motion of congruent instructions

### 2017-11-04 cgo/paper.tex
correction

\subsubsection{Reduce register pressure}
\label{hoist:reg-pressure}
Hoisting upwards will decrease the live-range of its use, if it is a last use (a
kill,) but increase the live-range of its definition. Conversely, sinking will
decrease the live-range of the defined register but increase the live-range for
killed operands. If the live-range after \gcm{} is less than before it will
be moved. Essentially, as long as there is one killed operand, code hoisting
will either decrease or preserve the register pressure.  Similarly, code-sinking
will either decrease or preserve the register pressure as long as there is one
operand killed at most.  The following example explains how \gcm{} of
identical computations can reduce the register pressure.

\begin{verbatim}
B0: b = m
    c = n
    if c is true then goto B3 else goto B4
B1: a0 = b<kill> + c<kill>
B2: a1 = b<kill> + c<kill>
\end{verbatim}

After hoisting, $a0$ and $a1$ are removed and a copy of $a0$ as $a1$ is placed
in $B0$ just before the branch. Since $b$ and $c$ are killed in $a0$ and $a1$,
hoisting the expressions will reduce the register pressure because two registers
will be freed.

@@

\subsubsection{Hoisting an expression across a call}
\label{cost:across-calls}
Even hoisting scalars across calls is tricky because it can increase the number
of spills. During the frame lowering of calls, the argument registers also known
as the caller saved registers are saved because they might be modified by the
callee and after the call they are restored. So before the call, the register
pressure is high because the number of available registers are reduced by the
number of caller saved registers. In that situation a computation that increases
register pressure is not profitable to hoist.

>>>>

\subsubsection{Reduce register pressure}
\label{hoist:reg-pressure}
Hoisting upwards will decrease the live-range of its use, if it is a last use (a
kill,) but increase the live-range of its definition. Conversely, sinking will
decrease the live-range of the defined register but increase the live-range for
killed operands. If the live-range after \GCM{} will decrease, it will be
moved. Essentially, as long as there is one killed operand, code hoisting will
either decrease or preserve the register pressure.  Similarly, code-sinking will
either decrease or preserve the register pressure as long as there is one
operand killed at most.  The following example explains how \GCM{} of can reduce
the register pressure.

\begin{verbatim}
B0: b = m
    c = n
    if c is true then goto B1 else goto B2
B1: a0 = b<kill> + c<kill>
    goto B3
B2: a1 = b<kill> + c<kill>
    goto B3
\end{verbatim}

After hoisting, $a0$ and $a1$ are removed and a copy of $a0$ is placed in
$B0$. Since $b$ and $c$ are killed in both $a0$ and $a1$, hoisting the
expressions will reduce the register pressure because two registers will be
freed at the insertion point but only one register will be required to assign
the definition of hoisted instruction $a0$.

@@

\subsubsection{Hoisting an expression across a call}
\label{cost:across-calls}
Even hoisting scalars across calls is tricky because it can increase the number
of spills. During the frame lowering of calls, the argument registers (also
known as the caller saved registers) are saved because they might be modified by
the callee and after the call they are restored. Due to this the register
pressure is high because the number of available registers are reduced by the
number of caller saved registers. In that situation a computation that increases
register pressure is not profitable to hoist.
